Hospitalizations for psychiatric conditions among adolescents during the COVID-19 pandemic

### 2021-08-18 psy_peds.Rmd
weekly count for distinct diseaasee groups distinct than mental

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- "2019-01-01"
history_end_date <- "2021-05-31"
pandemic_start_date <- "2020-03-15"
```

@@

ggsave("output/overall_weekly_count_all_comparison.png", width = 18, height = 9, units="cm")
```

>>>>

```{r}
# cut-off dates used in the analysis, these should not be changed
history_start_date <- "2017-01-01"
history_end_date <- "2021-05-31"
pandemic_start_date <- "2020-03-15"
```

@@

ggsave("output/overall_weekly_count_all_comparison.png", width = 18, height = 9, units="cm")
```
```{r}
icdCategory <- read.delim("public-data/icd10Codes.txt", header = FALSE, colClasses = "character")
colnames(icdCategory) <- c("icd_code_category", "icd_description_category")
patient_count_per_week_byCategory <- all_codes %>% 
  mutate( icd_code_category = ifelse(substr(concept_code, 1, 1) %in% c("D", "H"), substr(concept_code, 1, 2), substr(concept_code, 1, 1) ))

patient_count_per_week_byCategory <- left_join( patient_count_per_week_byCategory, icdCategory) %>%
  select(patient_num, cohort, weeks, icd_description_category, period) %>% 
  unique() %>%
  group_by(weeks, icd_description_category, period) %>%
  tally() %>%
  mutate(n = ifelse( n < obfuscation | isFALSE(obfuscation),
                     n,
                     0.5),
         siteid = site )

patient_count_per_week_byCategory %>%
  filter( icd_description_category %in% c("Neoplams","Diseases of the respiratory system", "Diseases of the nervous system", "Diseases of the digestive system", "Diseases of the blood", "Congenital malformations, deformations and chromosomal abnormalities" )) %>%
  ggplot(aes(x = weeks, y = n, fill = icd_description_category, color = icd_description_category)) +
  geom_point() +
  geom_line() +
  geom_vline(xintercept = as.Date(pandemic_start_date),
             linetype = "dashed") +
  scale_fill_manual(values = cbPalette) +
  scale_color_manual(values = cbPalette) +
  labs(y = "Counts",
       x = "Calendar Weeks",
       title = "Weekly patient counts") + 
  geom_smooth(method = "lm", formula = y ~ splines::ns(x, 2), se = TRUE, aes(colour=period), colour= "black", size = 0.5)

ggsave("output/overall_weekly_count_all_comparison_other_categories.png", width = 18, height = 9, units="cm")
